### 2019-08-16 reports/thesis/book.tex
Revise bib and intro
Format for Warwick thesis
Revise intro

\documentclass[12pt, a4paper]{memoir}
%\documentclass[12pt, a4paper, oldfontcommands]{memoir}
%\documentclass[12pt, a4paper]{report}

@@

\DeclareSIUnit\pixel{px}
\DeclareSIUnit\adu{ADU}

\begin{document}\sloppy

@@

\newpage
\tableofcontents*
\newpage
\listoffigures
\newpage
\listoftables

@@

Probability and statistics is used throughout in science. In particular, undergraduates are drilled to quote confidence intervals, use an appropriate number of significant figures and plot error bars in their studies. In physics, probability is used to model randomness in quantum mechanics and used to handle millions of particles in statistical mechanics.

@@

The aim of this thesis is to investigate if it is possible to do quality control of additive manufactured products using only a few x-ray projections to speed up the quality control process. By using fewer x-ray projections, uncertainty is introduced. This is where statistics comes in. It enables the sensible handling of uncertainty from sources of errors such as the random behaviour of x-ray photons to model misspecification of the problem.

The front cover shows the before and after of the statistical analysis. The left hand side shows an x-ray projection of an additive manufactured cuboid. Its edges appeared curved due to spot and panel effects and this can be fixed using shading correction. The right hand side shows the $p$-values of the resulting inference. Lighter colours shows evidence of a defect and they successfully highlighted voids put in there purposefully.

In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed. Sources of error were looked at and it was investigated to see how they were handled. In Chapter \ref{chapter2}, a test sample was additive manufactured and the chapter describes how experimental x-ray projections were obtained. Shading correction is explained here and it was used to remove sources of systematic errors in the projections. In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays. In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and methods were used to predict it. In Chapter \ref{chapter5}, statistical techniques were employed to look for defects in the test sample under the face of uncertainty. The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made. The thesis ends with an evaluation in Chapter \ref{chapter6}.

@@

In Chapter \ref{chapter5}, the replicated projections were split into two. 19 randomly selected projections were used for the variance-mean model to fit onto. The remaining projection was compared with the simulated projection under the face of uncertainty. The uncertainty was predicted using the variance-mean model. Inference was done on the test statistics, one for each pixel in a projection. Unfortunately, the simulation was not perfect which led to model misspecification, thus false positives. The empirical null filter was developed and used to smooth the test statistics. This allows the inference to pick out areas which are unusual and unlike its neighbours. The filtered test statistics was converted to $p$-values so that hypothesis testing can be done to detect the voids.

@@

Two angular projections were looked at in this thesis. The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection. Repeating the experiment using difficult angles may indicate weaknesses from using a singular angle. Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden in a particular angle.

The experiment could be improved if the location of the defects were known in the projection. This would allow identifying which positives are true positives and false positives and the analysis can be quantified using a ROC curve.

This thesis is a contribution to real-time quality control for additive manufacturing. A powerful multi-core computer could be used to conduct the statistical analysis of x-ray projections of AM products on a conveyor belt. By using fewer projections, quality control can be faster which advances the development and increase the scope of applications of additive manufacturing.

>>>>

\documentclass[12pt, a4paper, oneside]{memoir}
%oneside for soft copy
%twoside for hard final copy
\setlrmargins{4cm}{*}{*}
\checkandfixthelayout
%\documentclass[12pt, a4paper, oldfontcommands]{memoir}
%\documentclass[12pt, a4paper]{report}

@@

\DeclareSIUnit\pixel{px}
\DeclareSIUnit\adu{ADU}
\OnehalfSpacing*
\begin{document}\sloppy

@@

\cleardoublepage
\tableofcontents*
\cleardoublepage
\listoffigures
\cleardoublepage
\listoftables

@@

Probability and statistics is used throughout in science to handle data and uncertainty. In particular, undergraduates are drilled to quote confidence intervals, use an appropriate number of significant figures and plot error bars in their studies. In physics, probability is used to model randomness in quantum mechanics and used to handle millions of particles in statistical mechanics. Uncertainty is a daily occurrence.

@@

The aim of this thesis is to investigate if it is possible to do quality control of additive manufactured products using only a few x-ray projections to speed up the quality control process. By using fewer x-ray projections, uncertainty is introduced. This is where statistics comes in. It enables the sensible handling of uncertainty from sources of errors such as from the random behaviour of x-ray photons or from the model misspecification of the problem.

The front cover shows the before and after of the statistical analysis. The left hand side shows an x-ray projection of an additive manufactured cuboid. Its edges appeared curved due to spot and panel effects and this can be fixed using shading correction. The right hand side shows the $p$-values of the resulting inference. Lighter colours show evidence of a defect and they successfully highlighted voids put in there purposefully.

In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed. Sources of error were looked at and it was investigated to see how they were handled. In Chapter \ref{chapter2}, a test sample was additive manufactured and the chapter describes how experimental x-ray projections were obtained. Shading correction is explained here and it was used to remove sources of systematic errors in the projections. In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays. In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and generalised linear models were used to predict it. In Chapter \ref{chapter5}, statistical techniques were employed to look for defects in the test sample under the face of uncertainty. The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made. The thesis ends with an evaluation in Chapter \ref{chapter6}.

@@

In Chapter \ref{chapter5}, the replicated projections were split into two. 19 randomly selected projections were used for the variance-mean model to fit onto. The remaining projection was compared with the simulated projection under the face of uncertainty. The uncertainty was predicted using the variance-mean model. Inference was done on the test statistics, one for each pixel in a projection. Unfortunately, the simulation was not perfect which led to model misspecification, thus false positives. The empirical null filter was developed and used to smooth the test statistics. This allows the inference to pick out areas which are unusual and unlike its neighbours. The filtered test statistics were converted to $p$-values so that hypothesis testing can be done to detect the voids.

@@

Two angular projections were looked at in this thesis. The angles were selected by the engineers, in calibration with this experiment, so that all of the voids were visible in a single projection. Repeating the experiment using difficult angles may indicate weaknesses from using a singular angle. Perhaps this method could be extended by analysing more angular projections independently to pick up voids which may be hidden at a particular projection angle.

The experiment could be improved if the location of the defects were known in the projection. This would allow identifying which positives are true and false positives so that the analysis can be quantified using a ROC curve.

This thesis is a contribution to real-time quality control for additive manufacturing. A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt. By using fewer projections, quality control can be faster which advances the development and increase the scope of applications of additive manufacturing.
